Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2020-05-20 paper/zigzag.tex
use cite

\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
The right amount of disorder scatters long trajectories improves the Majorana properties~\onlinecite{Haim2019}, similar to the zigzag geometry cutting off these long trajectories.
We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
At $\phi=\pi$ we observe that zigzag outperforms disorder.

>>>>

\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
At $\phi=\pi$ we observe that zigzag outperforms disorder.
